\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2020-07-28 analysis/paper/paper.Rmd
Vetted lit-rev, fig and fig comments (cs3)

eval_introduction <- TRUE
eval_theory <- TRUE
eval_implementation <- TRUE
eval_cs1 <- TRUE
eval_cs2 <- TRUE
eval_cs3 <- TRUE
eval_cs4 <- TRUE
eval_colophon <- TRUE

@@

\textbf{Package}        & \textbf{Risks}  & \textbf{Non PH} & \textbf{Likelihood} & \textbf{Splines} & \textbf{Parametric} & \textbf{Parametric} & \textbf{Censoring} & \textbf{Risk}           \\

@@

\textbf{crrp}            & x                        &                           & x                     &                  &                     &                          &                                  &                                  \\

@@

\textbf{RiskRegression}  &                          &                           & x                     &                  &                     & x                        &                                  & x                                \\
\textbf{Rstpm2}          &                          & x                         & x                     & x                & x                   & x                        & x                                & x                         \\

@@

\caption{Comparison of various \proglang{R} packages for survival analysis based on several defining features.}

@@

# 1. Cox with only sps
coxSPS <- survival::coxph(Surv(time = d.time, event = death) ~ sps, 
                          data = train, x = TRUE)
abcoxSPS <- survival::survfit(coxSPS, newdata = test)
# 2. Cox with only aps
coxAPS <- survival::coxph(Surv(time = d.time, event = death) ~ aps, 
                          data = train, x = TRUE)
abcoxAPS <- survival::survfit(coxAPS, newdata = test)
# 3. Cox with everything but sps and aps
coxFull <- survival::coxph(Surv(time = d.time, event = death) ~ . - aps - sps, 
                           data = train, x = TRUE)
abcoxFull <- survival::survfit(coxFull, newdata = test)
# 4. Kaplan-Meier
KM <- survival::coxph(Surv(time = d.time, event = death) ~ 1, data = test)
abKM <- survival::survfit(KM)
abKMcompare <- data.frame(
  Time = abKM$time,
  KM = 1 - abKM$surv
)

@@

```{r baselines, echo=FALSE, eval=eval_cs3}
cox_ci <- ggplot(baseCoxComparisonData, aes(Time)) +
  geom_line(aes(y = APS, colour = "APS"), lwd = 1) +
  geom_line(aes(y = Full, col = "Full"), lwd = 1) +
  geom_line(aes(y = SPS, colour = "SPS"), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M")) + 
  paper_gg_theme
```

```{r brierpt1, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:brier1} Comparison of three Cox regression models. (A) Cumulative Incidence curves. (B) Time-dependent Brier scores."}
# Extract time points
times <- sort(unique(test$d.time))
# Compute Brier scores
brierAPS <- Score(list("PredictionModel" = coxAPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
brierSPS <- Score(list("PredictionModel" = coxSPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# First fix NA coefficients, then compute Brier score
coxFull$coefficients[which(is.na(coxFull$coefficients))] <- 0
brierFull <- Score(list("PredictionModel" = coxFull), data = test, 
                   formula = Surv(d.time, death != 0) ~ 1, summary = "ipa", 
                   se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# Combine all results for plotting
brierPlotter <- rbind(
  data.frame(brierScore = brierAPS$Brier$score$Brier[brierAPS$Brier$score$model == "PredictionModel"], 
             times = times, model = "APS"),
  data.frame(brierScore = brierFull$Brier$score$Brier[brierFull$Brier$score$model == "PredictionModel"], 
             times = times, model = "Full"),
  data.frame(brierScore = brierSPS$Brier$score$Brier[brierSPS$Brier$score$model == "PredictionModel"], 
             times = times, model = "SPS")
)

cox_brier <- ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4[1:3]) + 
  paper_gg_theme

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity."}
library(dotwhisker)
library(broom)
library(dplyr)

# extract coefficients for lollipop plot
estimatescoxNet <- setDT(as.data.frame(coef(coxNet)), 
                         keep.rownames = TRUE)

@@

estimatescb <- setDT(as.data.frame(coef(cbFull)[-c(1, 2), 1]), 
                     keep.rownames = TRUE)
# estimatescb$std.error<-0
estimatescb$Model <- "Pen. logistic"
colnames(estimatescb) <- c("term", "estimate", "model")

estimatescoxFull <- setDT(as.data.frame(coef(coxFull)), 
                          keep.rownames = TRUE)
# estimatescoxFull$std.error<-0
estimatescoxFull$Model <- "Cox"
colnames(estimatescoxFull) <- c("term", "estimate", "model")

@@

These values do not inform us of model performance. To do so, we take our hazard functions and use them to predict the absolute risk of everyone in our test set, over time. The probabilities over time for each individual are averaged, resulting in the absolute risk curves in Figure \ref{fig:cs3FinalBrier} (A). There is separation between the curves, but it is minimal. To better demonstrate the differences in performance between the models, we compare Brier scores over time. In Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our penalized logistic regression model compared to both Cox regression models. However, this difference is minimal. On the other hand, all three models outperform the Kaplan-Meier model.

```{r cs3Final, echo=FALSE, eval=eval_cs3}
reg_ci <- ggplot(ab, aes(Time)) +
  geom_line(data = baseCoxComparisonData, mapping = aes(y = Full, colour = "Cox"), lwd = 1) +
  geom_line(aes(y = absRisk, colour = Model), lwd = 1) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M"), lwd = 1) +
  labs(y = "Probability of Death", x = "Survival time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("Cox", "Penalized Cox", "Penalized logistic", "K-M")) + 
  paper_gg_theme
```

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} Four curves comparing the Cumulative Incidence (A) and the Brier scores (B) as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# Combine Brier scores between unpenalized and penalized models before plotting
data_brier <- bind_rows(
  brierFinalResults$Brier$score,
  filter(brierFull$Brier$score, model == "PredictionModel")
  ) %>% 
  mutate(model = case_when(
    model == "Null model" ~ "K-M",
    model == "PredictionModel" ~ "Cox",
    TRUE ~ model
  ),
  model = factor(model, levels = c("Cox", "Penalized Cox", "Penalized Logistic", "K-M"),
                 labels = c("Cox", "Pen. Cox", "Pen. Logistic", "K-M")))

reg_brier <- ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Survival time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  paper_gg_theme +  
  scale_color_manual(values = q4)

>>>>

eval_introduction <- TRUE
eval_theory <- TRUE
eval_implementation <- TRUE
eval_cs1 <- T
eval_cs2 <- T
eval_cs3 <- TRUE
eval_cs4 <- T
eval_colophon <- TRUE

@@

\textbf{Package}        & \textbf{Risks}  & \textbf{Non PH} & \textbf{Regression} & \textbf{Splines} & \textbf{Parametric} & \textbf{Parametric} & \textbf{Censoring} & \textbf{Risk}           \\

@@

\textbf{crrp}            & x                        &                           & x                     &                  &                     & x                        &                                  &                                  \\

@@

\textbf{RiskRegression}  & x                         &                           & x                     &                  &                     & x                        &                                  & x                                \\
\textbf{Rstpm2}          &                          & x                         &                      & x                & x                   & x                        & x                                & x                         \\

@@

\caption{Comparison of various \proglang{R} packages for survival analysis based on several defining features. Competing Risks: whether or not an implementation for competing risks is present. Allows Non-PH: permits models that can incorporate variables that change with survival time. Penalized Regression: allows for a penalty term when fitting the model. This is not restricted to lasso nor ridge. Splines: the package permits a flexible fit on time through the use of splines. Parametric: the package has implementations for parametric models. Semi-parametric: the package has implementations for semi-parametric models. Interval/left censoring: the package can interpret interval and left-censoring. If this is not selected, the package only handles right-censoring. Absolute Risk: the package has an implementation for survival curves, cumulative incidence or cumulative hazard rate functions to be plotted.}

@@

# 1. Cox with only sps
coxSPS <- survival::coxph(Surv(time = d.time, event = death) ~ sps, 
                          data = train, x = TRUE)
abcoxSPS <- survival::survfit(coxSPS, newdata = test)
# 2. Cox with only aps
coxAPS <- survival::coxph(Surv(time = d.time, event = death) ~ aps, 
                          data = train, x = TRUE)
abcoxAPS <- survival::survfit(coxAPS, newdata = test)
# 3. Cox with everything but sps and aps
coxFull <- survival::coxph(Surv(time = d.time, event = death) ~ . - aps - sps, 
                           data = train, x = TRUE)
abcoxFull <- survival::survfit(coxFull, newdata = test)
# 4. Kaplan-Meier
KM <- survival::coxph(Surv(time = d.time, event = death) ~ 1, data = test,x=TRUE)
abKM <- survival::survfit(KM)
abKMcompare <- data.frame(
  Time = abKM$time,
  KM = 1 - abKM$surv
)

@@

```{r baselines, echo=FALSE, eval=eval_cs3}
cox_ci <- ggplot(baseCoxComparisonData, aes(Time)) +
  geom_step(aes(y = APS, colour = "APS")) +
  geom_step(aes(y = Full, col = "Full")) +
  geom_step(aes(y = SPS, colour = "SPS")) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M")) +
  labs(y = "Probability of Death", x = "Follow-up time (Years)", color = "Models") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M")) + 
  paper_gg_theme
```

```{r brierpt1, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:brier1} Comparison of three Cox regression models to the unadjusted Kaplan-Meier curve. (A) Cumulative Incidence curves. For a given model, the plotted curve is the average curve of each individual in the study. Each follow-up time seen in the study was used. There are minimal differences between the curves. APS coincides with the SPS curve, as they are considerably overlapped.(B) Time-dependent Brier scores, where a lower score is better. The full model performs best overall."}
# Extract time points
times <- sort(unique(test$d.time))
# Compute Brier scores
brierAPS <- Score(list("PredictionModel" = coxAPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
brierSPS <- Score(list("PredictionModel" = coxSPS), data = test, 
                  formula = Hist(d.time, death != 0) ~ 1, summary = "ipa", 
                  se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# First fix NA coefficients, then compute Brier score
coxFull$coefficients[which(is.na(coxFull$coefficients))] <- 0
brierFull <- Score(list("PredictionModel" = coxFull), data = test, 
                   formula = Surv(d.time, death != 0) ~ 1, summary = "ipa", 
                   se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
brierNull <- Score(list("PredictionModel" = KM), data = test, 
                   formula = Surv(d.time, death != 0) ~ 1, summary = "ipa", 
                   se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)

# Combine all results for plotting
brierPlotter <- rbind(
  data.frame(brierScore = brierAPS$Brier$score$Brier[brierAPS$Brier$score$model == "PredictionModel"], 
             times = times, model = "APS"),
  data.frame(brierScore = brierFull$Brier$score$Brier[brierFull$Brier$score$model == "PredictionModel"], 
             times = times, model = "Full"),
  data.frame(brierScore = brierSPS$Brier$score$Brier[brierSPS$Brier$score$model == "PredictionModel"], 
             times = times, model = "SPS"),
    data.frame(brierScore = brierNull$Brier$score$Brier[brierNull$Brier$score$model == "PredictionModel"], 
             times = times, model = "K-M")
)

cox_brier <- ggplot(data = brierPlotter, mapping = aes(x = times, y = brierScore, col = model)) +
  geom_line() +
  xlab("Follow-up time (Years)") +
  ylab("Brier score") +
  labs(color = "Models") +
  # ggtitle("Brier scores over time") +
  scale_color_manual(values = q4, breaks = c("APS", "Full", "SPS", "K-M")) + 
  paper_gg_theme

@@

```{r coefplots, echo=FALSE, eval=eval_cs3, fig.cap="\\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity. Shrinkage occurs due to penalization."}
library(dotwhisker)
library(broom)
library(dplyr)

# extract coefficients for lollipop plot
estimatescoxNet <- data.table::setDT(as.data.frame(coef(coxNet)), 
                         keep.rownames = TRUE)

@@

estimatescb <- data.table::setDT(as.data.frame(coef(cbFull)[-c(1, 2), 1]), 
                     keep.rownames = TRUE)
# estimatescb$std.error<-0
estimatescb$Model <- "Pen. logistic"
colnames(estimatescb) <- c("term", "estimate", "model")

estimatescoxFull <- data.table::setDT(as.data.frame(coef(coxFull)), 
                          keep.rownames = TRUE)
# estimatescoxFull$std.error<-0
estimatescoxFull$Model <- "Cox"
colnames(estimatescoxFull) <- c("term", "estimate", "model")

@@

These values do not inform us of model performance. To do so, we take our hazard functions and use them to predict the absolute risk of everyone in our test set, over time. The probabilities over time for each individual are averaged, resulting in the absolute risk curves in Figure \ref{fig:cs3FinalBrier} (A). There is separation between the curves, but it is minimal. To better demonstrate the differences in performance between the models, we compare Brier scores over time. In Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our penalized logistic regression model compared to both Cox regression models. The differences, however, are minimal. All three outperform the Kaplan-Meier model.

```{r cs3Final, echo=FALSE, eval=eval_cs3}
reg_ci <- ggplot(ab, aes(Time)) +
  geom_step(data = baseCoxComparisonData, mapping = aes(x = Time,y = Full, colour = "Cox")) +
  geom_line(aes(y = absRisk, colour = Model)) +
  geom_step(data = abKMcompare, mapping = aes(x = Time, y = KM, color = "K-M")) +
  labs(y = "Probability of Death", x = "Follow-up time (Years)", color = "Models") +
  # ggtitle("Absolute risk curves") +
  scale_color_manual(values = q4, breaks = c("K-M","Cox","Penalized Cox","Penalized logistic")) + 
  paper_gg_theme
```

@@

```{r riskregressionBrier, echo = FALSE, eval = eval_cs3, fig.cap="\\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest results over follow-up time.", warning = FALSE}
# Compute Brier score for penalized models
brierFinalResults <- Score(list("Penalized Cox" = coxNet, "Penalized Logistic" = cbFull),
                           data = cbind(subset(test, select = c(d.time, death)),
                                        as.data.frame(newx)), 
                           formula = Hist(d.time, death != 0) ~ 1, summary = NULL, 
                           se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
#brierFinalResults$models<-as.character(brierFinalResults$models)
# Combine Brier scores between unpenalized and penalized models before plotting

data_brier <- bind_rows(
  brierFinalResults$Brier$score,
  filter(brierFull$Brier$score, model == "PredictionModel")
  )
data_brier$model<-factor(data_brier$model,c("Null model", "PredictionModel","Penalized Cox", "Penalized Logistic"))
levels(data_brier$model)<-c("Kaplan-Meier","Cox","Penalized Cox","Penalized logistic")

reg_brier <- ggplot(data = data_brier, mapping = aes(x = times, y = Brier, col = model)) +
  geom_line() +
  xlab("Follow-up time (Years)") +
  ylab("Brier score") +
  # ggtitle("Brier score over time") +
  labs(color = "Models") +
  paper_gg_theme +  
  scale_color_manual(values = q4)

### 2020-07-28 analysis/paper/paper.tex
Vetted lit-rev, fig and fig comments (cs3)

\caption{\label{fig:brier1} Comparison of three Cox regression models. (A) Cumulative Incidence curves. (B) Time-dependent Brier scores.}\label{fig:brierpt1}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3FinalBrier} (A). There is separation between the
curves, but it is minimal. To better demonstrate the differences in
performance between the models, we compare Brier scores over time. In
Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our
penalized logistic regression model compared to both Cox regression
models. However, this difference is minimal. On the other hand, all
three models outperform the Kaplan-Meier model.

@@

\caption{\label{fig:cs3FinalBrier} Four curves comparing the Cumulative Incidence (A) and the Brier scores (B) as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    794    760    736    722
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#>  time    
#>     0 0.0
#>   365 0.3
\end{CodeOutput}

\begin{CodeOutput}
#> [1] 0.2
\end{CodeOutput}
\end{CodeChunk}

@@

This report was generated on 2020-07-21 20:19:45 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.0 (2020-04-24)
#> Platform: x86_64-apple-darwin17.0 (64-bit)
#> Running under: macOS Catalina 10.15.5
#> 
#> Matrix products: default
#> BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib
#> LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib
#> 
#> locale:
#> [1] en_CA.UTF-8/en_CA.UTF-8/en_CA.UTF-8/C/en_CA.UTF-8/en_CA.UTF-8
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.5.6               dotwhisker_0.5.0         
#>  [3] timereg_1.9.4             glue_1.4.1               
#>  [5] scales_1.1.0              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_0.8.5              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.0.2               ggplot2_3.3.0            
#> [13] tidyverse_1.3.0           lubridate_1.7.8          
#> [15] visreg_2.6.1              tibble_3.0.1             
#> [17] riskRegression_2020.02.05 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.1-12          
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_3.0-2             
#> [25] Matrix_1.2-18             data.table_1.12.8        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0.9000      
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-2          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_1.13.3    base64enc_0.1-3    
#>  [7] fs_1.4.1            rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-0      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.6.1      cluster_2.1.0      
#> [19] dbplyr_1.4.3        png_0.1-7           compiler_4.0.0     
#> [22] httr_1.4.1          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.55       tools_4.0.0         gtable_0.3.0       
#> [31] Rcpp_1.0.4.6        cellranger_1.1.0    vctrs_0.3.1        
#> [34] nlme_3.1-147        iterators_1.0.12    xfun_0.15          
#> [37] rvest_0.3.5         lifecycle_0.2.0     polspline_1.1.17   
#> [40] muhaz_1.2.6.1       MASS_7.3-51.5       zoo_1.8-7          
#> [43] hms_0.5.3           sandwich_2.5-1      SparseM_1.78       
#> [46] RColorBrewer_1.1-2  rticles_0.14        yaml_2.2.1         
#> [49] gridExtra_2.3       rms_5.1-4           rpart_4.1-15       
#> [52] latticeExtra_0.6-29 stringi_1.4.6       foreach_1.5.0      
#> [55] checkmate_2.0.0     lava_1.6.7          shape_1.4.4        
#> [58] rlang_0.4.6         pkgconfig_2.0.3     evaluate_0.14      
#> [61] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [64] cmprsk_2.2-9        tidyselect_1.1.0    deSolve_1.28       
#> [67] R6_2.4.1            generics_0.0.2      Hmisc_4.4-0        
#> [70] multcomp_1.4-13     DBI_1.1.0           withr_2.2.0        
#> [73] pillar_1.4.4        haven_2.2.0         foreign_0.8-78     
#> [76] mgcv_1.8-31         nnet_7.3-13         mstate_0.2.12      
#> [79] modelr_0.1.6        crayon_1.3.4        rmarkdown_2.1      
#> [82] jpeg_0.1-8.1        grid_4.0.0          readxl_1.3.1       
#> [85] reprex_0.3.0        digest_0.6.25       webshot_0.5.2      
#> [88] numDeriv_2016.8-1.1 stats4_4.0.0        munsell_0.5.0      
#> [91] viridisLite_0.3.0   quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    editMax /Users/maxturgeon/Documents/git_repos/cbpaper
#> Head:     [2d08bac] 2020-07-20: Merge pull request #22 from sahirbhatnagar/write-popTime
\end{CodeOutput}
\end{CodeChunk}

>>>>

\caption{\label{fig:brier1} Comparison of three Cox regression models to the unadjusted Kaplan-Meier curve. (A) Cumulative Incidence curves. For a given model, the plotted curve is the average curve of each individual in the study. Each follow-up time seen in the study was used. There are minimal differences between the curves. APS coincides with the SPS curve, as they are considerably overlapped.(B) Time-dependent Brier scores, where a lower score is better. The full model performs best overall.}\label{fig:brierpt1}
\end{figure}
\end{CodeChunk}

@@

\caption{\label{fig:cs3lolliPlot} Lollipop plot showing the coefficient estimates between three models. If a coefficient estimate is 0 in any model, it is removed from the plot for simplicity. Shrinkage occurs due to penalization.}\label{fig:coefplots}
\end{figure}
\end{CodeChunk}

These values do not inform us of model performance. To do so, we take
our hazard functions and use them to predict the absolute risk of
everyone in our test set, over time. The probabilities over time for
each individual are averaged, resulting in the absolute risk curves in
Figure \ref{fig:cs3FinalBrier} (A). There is separation between the
curves, but it is minimal. To better demonstrate the differences in
performance between the models, we compare Brier scores over time. In
Figure \ref{fig:cs3FinalBrier} (B), the Brier score is lower in our
penalized logistic regression model compared to both Cox regression
models. The differences, however, are minimal. All three outperform the
Kaplan-Meier model.

@@

\caption{\label{fig:cs3FinalBrier} (A) Four curves comparing the probabilities of death as it changes over follow-up time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. All follow-up times seen in the new data were used. (B) Four curves demonstrating the Brier scores as they change over time between Cox regression, penalized Cox regression, penalized logistic regression, and Kaplan-Meier. Lower is better. Penalized logistic regression produced the lowest results over follow-up time.}\label{fig:riskregressionBrier}
\end{figure}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    491    459    444    445
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#>  time     
#>     0 0.00
#>   365 0.72
\end{CodeOutput}

\begin{CodeOutput}
#> [1] 0.65
\end{CodeOutput}
\end{CodeChunk}

@@

This report was generated on 2020-07-28 09:55:47 using the following
computational environment and dependencies:

@@

\begin{CodeOutput}
#> R version 4.0.2 (2020-06-22)
#> Platform: x86_64-pc-linux-gnu (64-bit)
#> Running under: Pop!_OS 20.04 LTS
#> 
#> Matrix products: default
#> BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.9.0
#> LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.9.0
#> 
#> locale:
#>  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
#>  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
#>  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
#>  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
#>  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
#> [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
#> 
#> attached base packages:
#> [1] splines   stats     graphics  grDevices utils     datasets  methods  
#> [8] base     
#> 
#> other attached packages:
#>  [1] broom_0.7.0               dotwhisker_0.5.0         
#>  [3] timereg_1.9.6             glue_1.4.1               
#>  [5] scales_1.1.1              forcats_0.5.0            
#>  [7] stringr_1.4.0             dplyr_1.0.0              
#>  [9] purrr_0.3.4               readr_1.3.1              
#> [11] tidyr_1.1.0               ggplot2_3.3.2            
#> [13] tidyverse_1.3.0           lubridate_1.7.9          
#> [15] visreg_2.7.0              tibble_3.0.3             
#> [17] riskRegression_2020.06.25 prodlim_2019.11.13       
#> [19] flexsurv_1.1.1            survival_3.2-3           
#> [21] pracma_2.2.9              magrittr_1.5             
#> [23] kableExtra_1.1.0          glmnet_4.0-2             
#> [25] Matrix_1.2-18             data.table_1.13.0        
#> [27] cowplot_1.0.0             colorspace_1.4-1         
#> [29] casebase_0.9.0           
#> 
#> loaded via a namespace (and not attached):
#>  [1] TH.data_1.0-10      VGAM_1.1-3          ellipsis_0.3.1     
#>  [4] ggstance_0.3.4      htmlTable_2.0.1     fs_1.4.2           
#>  [7] base64enc_0.1-3     rstudioapi_0.11     farver_2.0.3       
#> [10] MatrixModels_0.4-1  fansi_0.4.1         mvtnorm_1.1-1      
#> [13] xml2_1.3.2          codetools_0.2-16    knitr_1.29         
#> [16] Formula_1.2-3       jsonlite_1.7.0      cluster_2.1.0      
#> [19] dbplyr_1.4.4        png_0.1-7           compiler_4.0.2     
#> [22] httr_1.4.2          backports_1.1.8     assertthat_0.2.1   
#> [25] cli_2.0.2           acepack_1.4.1       htmltools_0.5.0    
#> [28] quantreg_5.61       tools_4.0.2         gtable_0.3.0       
#> [31] Rcpp_1.0.5          cellranger_1.1.0    vctrs_0.3.2        
#> [34] nlme_3.1-148        conquer_1.0.1       iterators_1.0.12   
#> [37] xfun_0.16           rvest_0.3.5         lifecycle_0.2.0    
#> [40] polspline_1.1.19    muhaz_1.2.6.1       MASS_7.3-51.6      
#> [43] zoo_1.8-8           hms_0.5.3           sandwich_2.5-1     
#> [46] SparseM_1.78        RColorBrewer_1.1-2  rticles_0.14       
#> [49] yaml_2.2.1          gridExtra_2.3       rms_6.0-1          
#> [52] rpart_4.1-15        latticeExtra_0.6-29 stringi_1.4.6      
#> [55] foreach_1.5.0       checkmate_2.0.0     lava_1.6.7         
#> [58] shape_1.4.4         mets_1.2.7.1        rlang_0.4.7        
#> [61] pkgconfig_2.0.3     matrixStats_0.56.0  evaluate_0.14      
#> [64] lattice_0.20-41     labeling_0.3        htmlwidgets_1.5.1  
#> [67] cmprsk_2.2-10       tidyselect_1.1.0    deSolve_1.28       
#> [70] plyr_1.8.6          R6_2.4.1            generics_0.0.2     
#> [73] Hmisc_4.4-0         multcomp_1.4-13     DBI_1.1.0          
#> [76] withr_2.2.0         pillar_1.4.6        haven_2.3.1        
#> [79] foreign_0.8-80      mgcv_1.8-31         nnet_7.3-14        
#> [82] mstate_0.2.12       modelr_0.1.8        crayon_1.3.4       
#> [85] rmarkdown_2.3       jpeg_0.1-8.1        grid_4.0.2         
#> [88] readxl_1.3.1        blob_1.2.1          reprex_0.3.0       
#> [91] digest_0.6.25       webshot_0.5.2       numDeriv_2016.8-1.1
#> [94] stats4_4.0.2        munsell_0.5.0       viridisLite_0.3.0  
#> [97] quadprog_1.5-8
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeOutput}
#> Local:    master /home/jesseislam/Documents/gits/cbpaper
#> Remote:   master @ origin (git@github.com:Jesse-Islam/cbpaper.git)
#> Head:     [d30ba8c] 2020-07-22: Merge pull request #23 from sahirbhatnagar/editMax
\end{CodeOutput}
\end{CodeChunk}
